### 2018-01-21 Sections/authors.tex
Minor APD stuff

\author{Peter P. Rohde}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\affiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\author{Jonathan P. Dowling}
\affiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

>>>>

\author{Peter P. Rohde}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\affiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\author{Jonathan P. Dowling}
\affiliation{Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}
\affiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, LA 70803, United States}

### 2018-01-21 Sections/models_for_quantum_computation.tex
Minor APD stuff

When using non-deterministic gates to prepare cluster states, there are approaches to nonetheless preparing ideal cluster states. There have been two main approaches that have become particularly well known.

The first is to use the ideas of \textit{micro-clusters}\index{Micro-clusters} and cluster state recycling\index{Cluster state recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walk}, which is biased in the direction of state growth. This approach is discussed in more detail in Sec.~\ref{sec:module}.

The second approach is to borrow ideas from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\text{defect}\leq \epsilon_\text{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

%
% Percolation Theory Techniques
%

\paragraph{Percolation theory techniques} \index{Percolation theory}

%
% Error Teleportation
%

\paragraph{Error teleportation}\label{sec:cs_error_tele}\index{Error teleportation}

\cite{RohdeMunroEtal}

>>>>

When using non-deterministic gates (i.e ones that probabilistically fail) to prepare cluster states, there are approaches to nonetheless preparing ideal cluster states. There have been two main approaches that have become particularly well known.

The first is to use the ideas of \textit{micro-clusters}\index{Micro-clusters} and cluster state recycling\index{Cluster state recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walk}, which is biased in the direction of state growth. This approach is discussed in more detail in Secs.~\ref{sec:CS_LO} \& \ref{sec:module}.

The second approach is to borrow techniques from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\text{defect}\leq \epsilon_\text{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

### 2018-01-21 Sections/physical_architectures_for_quantum_computing.tex
Minor APD stuff

To analyse the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single qubit clusters, which we assume `come for free'\footnote{As in beer.}). For example, the second element of the vector tell us how many 3-qubit linear clusters we have in our possession.

@@

\begin{figure*}[!htb]
\includegraphics[width=0.9\textwidth]{micro_clusters}
\caption{Linear, plus (+), and star micro-cluster states.}\label{fig:micro_clusters}\index{Linear micro-cluster states}\index{Plus micro-cluster states}\index{Star micro-cluster states}\index{Micro-cluster states}
\end{figure*}

@@

>>>>

To analyse the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single qubit clusters, which we assume `come for free'\footnote{As in beer.\index{Beer}}). For example, the second element of the vector tell us how many 3-qubit linear clusters we have in our possession.

@@

\begin{figure*}[!htb]
\includegraphics[width=0.8\textwidth]{micro_clusters}
\caption{Linear, plus (+), and star micro-cluster states.}\label{fig:micro_clusters}\index{Linear micro-cluster states}\index{Plus micro-cluster states}\index{Star micro-cluster states}\index{Micro-cluster states}
\end{figure*}

@@

%
% Error Teleportation
%

\paragraph{Error teleportation}\label{sec:cs_error_tele}\index{Error teleportation}

\comment{To do}

\cite{RohdeMunroEtal}

### 2018-01-21 Sections/protocols_for_the_quantum_internet.tex
Latin quote stubs
Minor APD stuff

The most common form of photo-detection is using avalanche photo-diodes (APDs)\index{Avalanche photo-diodes (APDs)}, which are cheap but non-number-resolving. Here a single photon excites an electron into the conduction band at a semiconductor junction, enabling a detectable current flow.

More recently, superconducting detectors\index{Superconducting photo-detectors} have been adopted, as they have the potential for number-resolution. Here a superconductor is kept just below its critical temperature, and the absorption of a photon is enough to heat the superconductor above the critical temperature, creating a detectable change in resistance across the superconductor. This is shown in Fig.~\ref{fig:super_det}. Despite their superior performance, however, superconducting detectors are very expensive (for obvious reasons) and only accessible to well-resourced labs.

@@

@@

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{detector_multiplexing}
\caption{Multiplexed number-resolved photo-detection using non-number-resolved photo-detectors. The principle is to spread out a multi-photon state across a large number of modes, sufficiently large that it is unlikely that more than one photon will be present in any given mode. Then, the sum of the number of clicks at each mode closely approximates the incident photon-number. (a) In the spatial domain. (b) In the temporal domain.} \label{fig:det_mult}
\end{figure}

@@

Finally, photo-detectors of all types are inevitably subject to `dark-counts'\index{Dark-counts}, whereby thermal noise, either within the detector or coupled from the noisy environment, triggers non-existent detection events. The distribution follows exactly that of the thermal state photon-number distribution (Sec.~\ref{sec:thermal_states}). Thus, the probability of $n$ dark-counts occurring is,
\begin{align} \index{Thermal distribution}
p_\text{dc}(n) = e^{-|\alpha|^2} \frac{|\alpha|^2}{n!},
\end{align}
where $\alpha$ is a parameterisation of the temperature of the environmental noise. Fortunately, modern detector technology is able to keep dark-count rates very low, making this far less of an issue than the aforementioned ones, loss being the dominant.

@@

%
% Detector Banks
%

\subsubsection{Detector banks} \index{Detector banks}

In the case of an entire quantum computation, whether it be in the circuit model or cluster state model, many qubits may need to be measured independently, adding a direct multiplicative overhead in the required number of detectors. Furthermore, in protocols requiring fast-feedforward, the detectors may be required to have very fast time-response. These requirements can quickly become very challenging and expensive, further exaggerating the desirability of outsourcing the measurement stage.

\comment{Using multiplexing to reuse single detector}

>>>>

%
% Avalanche Photo-Diodes (APDs)
%

\paragraph{Avalanche photo-diodes}\index{Avalanche photo-diodes (APDs)}

The most common form of photo-detection is using avalanche photo-diodes (APDs), which are cheap but non-number-resolving. Here a single photon excites an electron into the conduction band at a semiconductor junction, enabling a detectable current flow. However, a single excitation triggers an `avalanche' of further excitation making the magnitude of the detected current essentially unrelated to exact photon number.

%
% Superconducting Photo-Detectors}
%

\paragraph{Superconducting photo-detectors}\index{Superconducting photo-detectors}

More recently, superconducting detectors have been adopted, as they have the potential for number-resolution. Here a superconductor is kept just below its critical temperature, and the absorption of a photon is enough to heat the superconductor above the critical temperature, creating a detectable change in resistance across the superconductor. This is shown in Fig.~\ref{fig:super_det}. Despite their superior performance, however, superconducting detectors are very expensive (for obvious reasons) and only accessible to well-resourced labs. However, unlike APDs they can be photon-number-resolving.

@@

\comment{Is this the same as transition edge sensor (TES)}

%
% Quantum Dot Photo-Detectors
%

\paragraph{Quantum dot photo-detectors}\index{Quantum dot photo-detectors}

\comment{To do}

%
% Photo-Diodes
%

\paragraph{Photo-diodes}\index{Photo-diodes}

\comment{To do}

%
% Experimental issues
%

\paragraph{Experimental issues}

@@

@@

Photo-detectors of all types are inevitably subject to `dark-counts'\index{Dark-counts}, whereby thermal noise\index{Thermal noise}, either within the detector or coupled from the noisy external environment, triggers non-existent detection events. The distribution follows exactly that of the thermal state photon-number distribution (Sec.~\ref{sec:thermal_states}). Thus, the probability of $n$ dark-counts occurring is,
\begin{align} \index{Thermal distribution}
p_\text{dc}(n) = e^{-|\alpha|^2} \frac{|\alpha|^2}{n!},
\end{align}
where $\alpha$ is a parameterisation of the temperature of the environmental noise. Fortunately, modern detector technology is able to keep dark-count rates very low, making this far less of an issue than the aforementioned ones, loss being the dominant.

Finally, all photo-detection techniques are subject to some degree of `time-jitter'\index{Time-jitter} -- noise in the detector's reported time of detection. This can be extremely important in the context of temporal mode-matching, where post-selection upon detection events in an extremely narrow time-window effectively enforces temporal indistinguishability.

%
% Multiplexed Photo-Detection
%

\subsubsection{Multiplexed photo-detection}\index{Multiplexed photo-detection}

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{detector_multiplexing}
\caption{Multiplexed number-resolved photo-detection using non-number-resolved photo-detectors. The principle is to spread out (as uniformly as possible) a multi-photon state across a large number of modes, sufficiently large that it is unlikely that more than one photon will be present in any given mode. Then, the sum of the number of clicks at each mode closely approximates the incident photon-number. (a) In the spatial domain. (b) In the temporal domain. The advantage of employing the temporally multiplexed architecture is that only a single detector is required, unlike the $N$ detectors required in the spatially multiplexed scheme. However this requires that the dead-time\index{Dead-time} of the detector is less than the round-trip time of the fibre loop.} \label{fig:det_mult}
\end{figure}

@@
